A Review on Multi-Label Learning Algorithms

### 2018-01-17 Paper/Presentation/mll_review.tex
update presentation and paper report
Update presentation

\end{itemize}
%TODO: Include stuff about multi-labeled dataset characterization?
\end{frame}
%------------------------------------------------
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item[$\triangleright$] e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

@@

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at feature $l$ s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Relevant-nonrelevant label pairs of $x_i$ $(y_j,y_k) \in Y_i \times \bar Y_i$ are separated by a function of their classifiers $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] Retrieves a ranked list of label pairs for each unseen instance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\end{itemize}
TODO : details of operation ixta
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Labels encoded as binary random vectors into a joint pdf
\item[$\bullet$] Label correlations encoded into the joint pdf as constraints
\item[$\bullet$] Model via the maximum information entropy criterion: $H_p(x, y)$, subject to constraints $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set
\item[$\bullet$] Objective arrived by Lagrange multipliers, solvable by any constraint optimization solver
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} P(y | x)$
\end{itemize}
how the fuck
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning Todoooo
\begin{itemize}
\item[$\circ$] Each ML example described by a bag of instances while associated with a single/binary label
\item[$\circ$] Models the object’s complex semantics in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification Todoooo
\begin{itemize}
\item[$\circ$] Model class co-relevance in a (vague) graded membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\end{itemize}
\end{frame}
%------------------------------------------------
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item[$\triangleright$] e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

@@

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at feature $l$ s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Relevant-nonrelevant label pairs of $x_i$ $(y_j,y_k) \in Y_i \times \bar Y_i$ are separated by a function of their classifiers $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] Retrieves a ranked list of label pairs for each unseen instance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\end{itemize}
TODO : details of svm operation
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Labels encoded as binary random vectors into a joint pdf
\item[$\bullet$] Label correlations encoded into the joint pdf as constraints
\item[$\bullet$] Model via the maximum information entropy criterion: $H_p(x, y)$, subject to constraints $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set
\item[$\bullet$] Objective arrived by Lagrange multipliers, solvable by any constraint optimization solver
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} P(y | x)$
\end{itemize}
how the fuck
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning
  % https://en.wikipedia.org/wiki/Multiple-instance_learning
\begin{itemize}
\item[$\circ$] Instead of labeled instances, get binary-labeled \emph{bags of instances}
\item[$\circ$] Assign positive label to bag if at least one member is positive
\item[$\circ$] Models complex semantics of $x_i$ in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification
  % https://en.wikipedia.org/wiki/Ordinal_regression
\begin{itemize}
\item[$\circ$] Assume labels are related through a natural ordering
\item[$\circ$] Instead of explicit class relevance, assume an ordering of
  relevance between labels via a membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}
